\documentclass[11pt]{article}
\usepackage[total={7in, 9in}]{geometry}
\usepackage[hidelinks]{hyperref}

\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[-] #1}
}

\begin{document}

\begin{center}
{\LARGE\bfseries Nicholas Balasus}\\[3mm]
\href{mailto:nicholasbalasus@g.harvard.edu}{nicholasbalasus@g.harvard.edu}\\
\href{https://nicholasbalasus.github.io}{nicholasbalasus.github.io}\\
\textit{Updated \today}
\end{center}

\section*{Education}
\begin{itemize}
    \itemsep0em 
    \item Ph.D. Student in Environmental Science and Engineering\\
    Harvard University, Advisor: Daniel Jacob\\
    September 2021 -- Present
    \item Bachelor of Science in Chemical Engineering\\
    University of Maryland, Baltimore County (UMBC)\\
    September 2017 -- May 2021
\end{itemize}

\section*{Research}
\begin{itemize}
    \itemsep0em 
    \item Graduate Research Assistant\\
    Harvard University, Advisor: Daniel Jacob\\
    September 2021 -- Present
    \item Undergraduate Research Assistant\\
    UMBC, Advisor: Christopher Hennigan\\
    September 2017 -- August 2021
    \item Undergraduate Research Assistant\\
    NOAA GFDL, Advisor: Fabien Paulot\\
    May 2020 -- August 2020
\end{itemize}

\section*{Publications}
\begin{itemize}
    \itemsep0em 
    \item Oak, Y.J., D.J. Jacob, \textbf{N. Balasus}, L.H. Yang, H. Chong, J. Park, H. Lee, G.T. Lee, E.S. Ha, R.J. Park, H. Kwon, J. Kim (submitted). A bias-corrected GEMS geostationary satellite product for nitrogen dioxide using machine learning to enforce consistency with the TROPOMI satellite instrument.
    \item East, J.D., D.J. Jacob, \textbf{N. Balasus}, A.A. Bloom, L. Bruhwiler, Z. Chen, J.O. Kaplan, L.J. Mickley, T.A. Mooring, E. Penn, B. Poulter, M.P. Sulprizio, R.M. Yantosca, J.R. Worden, Z. Zhang (submitted). Interpreting the seasonality of atmospheric methane.
    \item Varon, D.J., D. Jervis, S. Pandey, S.L. Gallardo, \textbf{N. Balasus}, L.H. Yang, and D.J. Jacob (submitted). Quantifying NO$_x$ point sources with Landsat and Sentinel-2 satellite observations of NO$_2$ plumes.
    \item Chen, Z., \textbf{N. Balasus}, H. Lin, H. Nesser, and D.J. Jacob (2024). African rice cultivation linked to rising methane. \textit{Nat. Clim. Chang.}, \href{https://doi.org/10.1038/s41558-023-01907-x}{https://doi.org/10.1038/s41558-023-01907-x}.
    \item Watine-Guiu, M., D.J. Varon, I. Irakulis-Loitxate, \textbf{N. Balasus}, and D.J. Jacob (2023). Geostationary satellite observations of extreme and transient methane emissions from oil and gas infrastructure. \textit{Proc. Natl. Acad. Sci.}, \href{https://doi.org/10.1073/pnas.2310797120}{https://doi.org/10.1073/pnas.2310797120}.
    \item \textbf{Balasus, N.}, D.J. Jacob, A. Lorente, J.D. Maasakkers, R.J. Parker, H. Boesch, Z. Chen, M.M. Kelp, H. Nesser, and D.J. Varon (2023). A blended TROPOMI+GOSAT satellite data product for atmospheric methane using machine learning to correct retrieval biases. \textit{Atmos. Meas. Tech.}, \href{https://doi.org/10.5194/amt-16-3787-2023}{https://doi.org/10.5194/amt-16-3787-2023}.
    \item Battaglia Jr., M.A., \textbf{N. Balasus}, K. Ball, V. Caicedo, R. Delgado, A.G. Carlton, and C.J. Hennigan (2021). Urban aerosol chemistry at a land-water transition site during summer - Part 2: Aerosol pH and liquid water content. \textit{Atmos. Chem. Phys.}, \href{https://doi.org/10.5194/acp-21-18271-2021}{https://doi.org/10.5194/acp-21-18271-2021}.
    \item \textbf{Balasus, N.}, M.A. Battaglia Jr., K. Ball, V. Caicedo, R. Delgado, A.G. Carlton, and C.J. Hennigan (2021). Urban aerosol chemistry at a land-water transition site during summer - Part 1: Impact of agricultural and industrial ammonia emissions. \textit{Atmos. Chem. Phys.}, \href{https://doi.org/10.5194/acp-21-13051-2021}{https://doi.org/10.5194/acp-21-13051-2021}.
\end{itemize}

\section*{Presentations}
\begin{itemize}
    \itemsep0em
    \item \textbf{Balasus, N.}, D.J. Jacob, A. Lorente, J.D. Maasakkers, R.J. Parker, H. Boesch, Z. Chen, M.M. Kelp, H. Nesser, and D.J. Varon (2023). A blended TROPOMI+GOSAT satellite data product for atmospheric methane using machine learning to correct retrieval biases (Oral). \textit{AGU Fall Meeting}, San Francisco, CA.
    \item \textbf{Balasus, N.}, F. Paulot, S. Burrows, L.W. Horowitz, and C. Stock (2021). Representation of Marine Organic Aerosols in the GFDL Earth System Model (Poster). \textit{American Meteorological Society Meeting}, Virtual.
    \item \textbf{Balasus, N.}, M.A. Battaglia Jr., K. Ball, R. Delgado, and C.J. Hennigan (2019). Characterizing the Impact of Poultry and Cattle Farms on Chesapeake Bay Aerosols in Baltimore, MD During the OWLETS-2 Campaign (Oral). \textit{EPA International Emissions Inventory Conference}, Dallas, TX.
    \item \textbf{Balasus, N.}, M.A. Battaglia Jr., K. Ball, R. Delgado, and C.J. Hennigan (2019). Investigating the Acidity and Liquid Water Content of Atmospheric Particles on the Chesapeake Bay during the OWLETS-2 Campaign (Poster). \textit{American Meteorological Society Meeting}, Phoenix, AZ.
\end{itemize}

\section*{Teaching Experience}
\begin{itemize}
    \itemsep0em 
    \item Professional Writing for Scientists and Engineers\\
    Teaching Assistant for Fall 2023 and Spring 2024 at Harvard University
    \item Confronting Climate Change: A Foundation in Science, Technology and Policy\\
    Teaching Assistant for Fall 2022 at Harvard University
    \item Chemical Process Control and Safety\\
    Teaching Assistant for Spring 2021 at UMBC
    \item Chemical Process Thermodynamics\\
    Teaching Assistant for Fall 2020 at UMBC
    \item Chemical Engineering Problem Solving and Experimental Design Lab\\
    Teaching Assistant for Spring 2020 at UMBC
    \item Chemical Engineering Analysis\\
    Teaching Assistant for Fall 2019 at UMBC
\end{itemize}

\section*{Awards and Honors}
\begin{itemize}
    \itemsep0em 
    \item DoD National Defense Science and Engineering Graduate (NDSEG) Fellowship\\
    September 2022 -- Present
    \item UMBC Chemical, Biochemical, and Environmental Engineering Undergraduate Research Award\\
    May 2021
    \item NOAA Ernest F. Hollings Undergraduate Scholarship Recipient\\
    May 2019 -- May 2021
\end{itemize}

\section*{Service}
\begin{itemize}
    \itemsep0em 
    \item Reviewer for \textit{Atmospheric Measurement Techniques}, \textit{Remote Sensing of Environment}
\end{itemize}

\end{document}
